Modelling last glacial cycle ice dynamics in the Alps

### 2017-01-31 articles/cycle/alps-cycle.tex
Add ideas from Frank and Matthias in the text.

@@

@@

>>>>

    \idea{Matthias: I think it is very important to emphasize the knowledge gap
          that you fill in with your work in the Intro. (1) it is incompletely
          known how many advances occurred during the Last glacial cycle, (2)
          what drove the different response of the individual lobes (you show
          that it is glacier response time, i.e. ice dynamics), (3) how the
          temporal dynamics of subglacial erosion was structured.}

@@

    \idea{Matthias: The selection of figures in the main text and SOM is good.
          I find Figure 2 quite difficult to understand at first glance. I
          would combine it (already before submission) with Fig. 3. the Figure
          can then focus both on the temporal advance/retreat patterns of the 4
          lobes (four panels on the left side of figure) and the spatial
          differences in max. ice elevation (1 panel on right side of figure,
          with centerlines indicated). I would have the one with trimline
          elevation again in the Supplementary.}

@@

    \idea{Frank: I would keep this topic for another paper.}
